Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-03-08 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added citations

\begin{itemize_2pt}
	\item Heterogeneity in mgmt practices across mid-sized and large firms \textcolor{camel}{(Bloom et al., 2007, Bloom et al., 2010, Syverson, 2011)}
\end{itemize_2pt}
\end{frame}

@@

		\item 2 general conceptualizations of business practices
		\begin{enumerate_2pt}
			\item As factor of production $\textcolor{bdf}{B}$ chosen by owner at market price $\textcolor{red}{p_{B}}$
			\item As technology affecting productivity factor $\textcolor{red}{A}$
			\item[] See, e.g., \textcolor{camel}{Bloom et al., (2016), McKenzie and Woodruff (2017)} %Quinn2019}
		\end{enumerate_2pt}

@@

	\item \normalsize Further specific channels of potential impact
	\begin{enumerate_2pt}
		\item Better \textcolor{bdf}{negotiation practices} may affect raw material prices $\textcolor{red}{s}$
		\item \textcolor{bdf}{Record-keeping} and \textcolor{bdf}{financial planning practices} may affect borrowing constraints $\textcolor{red}{\lambda}$ through banks' willingness to lend (see, e.g., \textcolor{camel}{Bruhn and Zia, 2013})
		\item \textcolor{bdf}{Marketing practices} may affect output price $\textcolor{red}{p}$ by changing demand

@@

	\item Average training program not inexpensive (USD 177 per person for ILO training, \citet{Lieshout2017})
	\item[] $\rightarrow$ Typical training program \textcolor{bdf}{highly subsidized}
	\item[] \quad (Median contribution 10\% of full price)

@@

\begin{frame}
\frametitle{Impact on Performance}
First wave of evaluations
	\begin{itemize_2pt}
	\item  Headline result: \textcolor{bdf}{No impact on business performance}
	\begin{itemize_2pt}
		\item Modest short-term adoption of practices (long-term fade-out)
		\item Null-effect on business sales and profits
		\item Early examples: \textcolor{camel}{Karlan and Valdivia, 2011, Bruhn and Zia, 2013; Giné and Mansuri, 2014; Field, et al., 2010} 
		%\item Later examples: \textcolor{camel}{Bulte et al., 2017; Anderson, Chandy, and Zia, 2018}

@@

\begin{frame}
\frametitle{Targeted Training}
	Female entrepreneurs
	\begin{itemize_2pt}
		\item Examples: 
		\begin{itemize_2pt}
			\item Gender and Enterprise Together (GET Ahead, ILO; \textcolor{camel}{Bulte et al., 2017}, \textcolor{camel}{McKenzie and Puerto, 2021})
			\item Start and Improve Your Business (SIYB, IFC; \textcolor{camel}{de Mel et al., 2014})
		\end{itemize_2pt}
		\item \textcolor{bdf}{Most common type of targeted training} (complementary to classical microfinance model)

@@

		\item Structural reasons
		\begin{itemize_2pt}
			\item Women overrepresented in subsistence entrepreneurship
			\item Female entrepreneurs often subject to more severe constraints (e.g., due to household-level reallocation; see, e.g., \textcolor{camel}{Bernhardt et al. 2019}, \textcolor{camel}{de Mel et al., 2009})
		\end{itemize_2pt}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	Young entrepreneurs
	\begin{itemize_2pt}
		\item Typically embedded as \textcolor{bdf}{entrepreneurship courses in school or university} (business concepts and soft skills)
		\item Example: Final year university course in Tunisia \textcolor{camel}{(Alaref et al., 2020)}
		\begin{itemize_2pt}
			\item Positive impact on business entry tapers off after 4 years
		\end{itemize_2pt}
	\end{itemize_2pt}

@@

High-growth businesses ("gazelles")
\begin{itemize_2pt}
	\item Extensive-margin prediction of future MSE growth is hard \textcolor{camel}{(Fafchamps and Woodruff, 2017)} 
	\begin{itemize_2pt}
		\item Survey, ability measure, expert panel all explain unique variation
		\item But: Business training for predicted gazelles shows no impact
	\end{itemize_2pt}

@@

	\item Small literature on business accelerators and incubators
	\begin{itemize_2pt}
		\item See, e.g., \textcolor{camel}{Cusolito et al., 2020}, \textcolor{camel}{Gonzalez-Uribe et al., 2017}, \textcolor{camel}{Gonzalez-Uribe et al. 2020}
	\end{itemize_2pt}
\end{itemize_2pt}

@@

	\item Aspiration interventions can backfire
	\begin{itemize_2pt}
		\item Goal setting intervention resulted in \textit{lower} investment \citep{McKenzieYang2021}
		\item[] $\rightarrow$ Potential of aspiration frustration if external constraints bind 
		\item[] \quad \citep[see also,][]{Galiani2018}
	\end{itemize_2pt}

>>>>

\begin{itemize_2pt}
	\item Heterogeneity in mgmt practices across mid-sized and large firms \textcolor{camel}{\citep{Bloom2007, Bloom2010, Syverson2011}}
\end{itemize_2pt}
\end{frame}

@@

		\item 2 general conceptualizations of business practices
		\begin{enumerate_2pt}
			\item As factor of production $\textcolor{bdf}{B}$ chosen by owner at market price $\textcolor{red}{p_{B}}$
			\item As technology affecting productivity factor $\textcolor{red}{A}$
			\item[] \citep[See, e.g.,][]{Bloom2016, McKenzie2017}
		\end{enumerate_2pt}

@@

	\item \normalsize Further specific channels of potential impact
	\begin{enumerate_2pt}
		\item Better \textcolor{bdf}{negotiation practices} may affect raw material prices $\textcolor{red}{s}$
		\item \textcolor{bdf}{Record-keeping} and \textcolor{bdf}{financial planning practices} may affect borrowing constraints $\textcolor{red}{\lambda}$ through banks' willingness to lend \citep[see, e.g.][]{Bruhn2013}
		\item \textcolor{bdf}{Marketing practices} may affect output price $\textcolor{red}{p}$ by changing demand

@@

	\item Average training program not inexpensive (USD 177 per person for ILO training, \citet{vanLieshout2017})
	\item[] $\rightarrow$ Typical training program \textcolor{bdf}{highly subsidized}
	\item[] \quad (Median contribution 10\% of full price)

@@

\begin{frame}
\frametitle{Impact on Performance}
First wave of evaluations
	\begin{itemize_2pt}
	\item  Headline result: \textcolor{bdf}{No impact on business performance}
	\begin{itemize_2pt}
		\item Modest short-term adoption of practices (long-term fade-out)
		\item Null-effect on business sales and profits
		\item Early examples: \citet{Field2010, Karlan2011, Bruhn2013}, also \citet[][WP in 2014]{Gine2021}

@@

\begin{frame}
\frametitle{Targeted Training}
	Female entrepreneurs
	\begin{itemize_2pt}
		\item Examples: 
		\begin{itemize_2pt}
			\item Gender and Enterprise Together \citep[GET Ahead, ILO;][]{Bulte2017, McKenziePuerto2021}
			\item Start and Improve Your Business \citep[SIYB, IFC;][]{deMel2014}
		\end{itemize_2pt}
		\item \textcolor{bdf}{Most common type of targeted training} (complementary to classical microfinance model)

@@

		\item Structural reasons
		\begin{itemize_2pt}
			\item Women overrepresented in subsistence entrepreneurship
			\item Female entrepreneurs often subject to more severe constraints; e.g., due to household-level reallocation \citep[see, e.g.,][]{Bernhardt2019, deMel2009a}
		\end{itemize_2pt}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	Young entrepreneurs
	\begin{itemize_2pt}
		\item Typically embedded as \textcolor{bdf}{entrepreneurship courses in school or university} (business concepts and soft skills)
		\item Example: Final year university course in Tunisia \citep{Alaref2020}
		\begin{itemize_2pt}
			\item Positive impact on business entry tapers off after 4 years
		\end{itemize_2pt}
	\end{itemize_2pt}

@@

High-growth businesses ("gazelles")
\begin{itemize_2pt}
	\item Extensive-margin prediction of future MSE growth is hard \citep{Fafchamps2017}
	\begin{itemize_2pt}
		\item Survey, ability measure, expert panel all explain unique variation
		\item But: Business training for predicted gazelles shows no impact
	\end{itemize_2pt}

@@

	\item Small literature on business accelerators and incubators
	\begin{itemize_2pt}
		\item \citet{Cusolito2021, GonzalezUribe2018, GonzalezUribe2021}
	\end{itemize_2pt}
\end{itemize_2pt}

@@

	\item Aspiration interventions can backfire
	\begin{itemize_2pt}
		\item Goal setting intervention resulted in \textit{lower} investment \citep{McKenzie2021a}
		\item[] $\rightarrow$ Potential of aspiration frustration if external constraints bind 
		\item[] \quad \citep[see also,][]{Galiani2018}
	\end{itemize_2pt}
